Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-24 paper/paper.tex
eliminated abstract (page limit). finished up pantilt writing

\documentclass[10pt]{report}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=cyan
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{listings}
\usepackage{float}
\usepackage{textcomp}
\usepackage{multicol}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\itemspace}{	\setlength{\itemsep}{0cm} \setlength{\parskip}{0cm}}
\newcommand{\degrees}[1]
{
\begin{math}
#1^{\circ} 
\end{math}
}
\hyphenation{auto-nomous construction}

@@

\begin{abstract}
We will write the abstract after the rest of the paper is finished. If we're really close to the page limit, we may be able to omit it.
\end{abstract}

@@

\begin{figure}
	\centering
	\subfloat[Isometric View]{\label{fig:pantilt_isometric} 
			\includegraphics[width=0.75\textwidth]{../images/pantilt_isometric.png}}
\\
	\subfloat[Side View.]{\label{fig:pantilt_side} 
			\includegraphics[width=0.75\textwidth]{../images/pantilt_side.png}}
	\caption{Pan Tilt Unit}
	\label{fig:pantilt}
\end{figure}
\begin{figure}
	\subfloat[Linkage Detail View]{\label{fig:pantilt_linkdetail} 
			\includegraphics[width=0.6\textwidth]{../images/pantilt_linkdetail.png}}
	\subfloat[Linkage Velocity Plots]{\label{fig:pantilt_linkdetail} 
			\includegraphics[width=0.4\textwidth]{../images/pantilt_linkplot.png}}
	\caption{Tilt Linkage Detail}
	\label{fig:pantilt_link}
\end{figure}

@@

We took advantage of the MHS-PM5's swiveling lens assembly 
(see Figure \ref{fig:camera_frontview}, and added a servo actuator which could rotate the lens \degrees{135} back from straight forward, as shown in Figure \ref{fig:pantilt_linkdetail}. The tilt servo is a Hitech HS 77BB \ref{hitechs77bb}, and is capable of \degrees{180} rotation.
The camera and tilt servo assembley is attached to the aircraft on a rotating mount. A thrust bearing takes lateral loads off the pan servo shaft, and stabilizes the assembly. The pan servo is a Hitech HS 785HB \ref{hitechhs785}, and is capable of \degrees{720} rotation. Both servos are powered and controlled by the Camera Control board.

The total height of the imaging system is 8.75", only 4'' of which is exposed below the fuselage of the aircraft. The rotating assembly is, on its widest dimension 2.13", and would fit inside a 2.5" cylinder. Wires exiting the side of the camera, inside the fuselage, may make the assembly a bit wider. Because the maximum rotation is only \degrees{270}, the camera and tilt servo wires only have to be capable of wrapping \degrees{\pm 360} around the shaft below the thrust bearing. A wire guide will be added to keep the wires from tangling once construction of the pan-tilt is complete.

@@

\newpage
\appendix
\renewcommand\thesection{Appendix \Alph{section}}
\section{Pre-flight Procedures}
\label{sec:appendix_preflight}
\begin{enumerate}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item Assemble plane.
	\item Check all mechanical and electrical connections.
		\begin{itemize}
		\itemspace
		\item Are all nuts/bolts loc-tited?
		\item Are all servo extensions connected and properly secured?
		\item Are all access hatches secured?
		\end{itemize}
	\item Position wingmen\footnotemark, centerman\footnotemark.
	\item Pilot turns on transmitter, announces ``transmitter on.''
	\item Pilot requests ``receiver on''.  Centerman turns on receiver, acknowledges.
	\item Pilot completes surface checks:
		\begin{itemize}
		\itemspace
		\item Ailerons
		\item Elevator
		\item Rudder
		\item Throttle
		\end{itemize}
	\item Starter primes engine.
	\item Pilot obtains visual and verbal confirmation that wingmen, centerman are in place and alert.
	\item Pilot requests ``ignition on.''  Centerman moves ignition switch to the ``on'' position and acknowledges.
	\item Starter requests ``prop clear.''  Starter obtains visual confirmation that no person is standing in the prop arc and announces ``prop clear.''
	\item Starter announces ``contact'' and starts the engine.
	\item Starter clears the area.
	\item Pilot repeats surface and throttle checks at close range.
	\item Pilot leaves starting area and performs surface and throttle checks from a distance (range test).
	\item Pilot returns to starting area to prepare for taxi.
	\item Pilot requests ``centerman off.''  Centerman carefully clears the area and acknowledges.
	\item Pilot requests ``wingmen off.''  Wingmen carefully clear the area and acknowledge.
	\item Pilot taxis airplane to appropriate location to begin takeoff.
	\item Pilot commences takeoff.

>>>>

\documentclass[10pt]{report}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=blue
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{listings}
\usepackage{float}
\usepackage{textcomp}
\usepackage{multicol}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\itemspace}{	\setlength{\itemsep}{0cm} \setlength{\parskip}{0cm}}
\newcommand{\degrees}[1]
{
\begin{math}
#1^{\circ} 
\end{math}
}
\hyphenation{auto-nomous construction}

@@

% We are definitely going to hit the page limit. No more abstract.
%\begin{abstract}
%We will write the abstract after the rest of the paper is finished. 
%If we're really close to the page limit, we may be able to omit it.
%\end{abstract}

@@

\begin{figure}
	\centering
	\subfloat[Isometric View]{\label{fig:pantilt_isometric} 
			\includegraphics[width=0.75\textwidth]{../images/pantilt_isometric.png}}
\\
	\subfloat[Side View.]{\label{fig:pantilt_side} 
			\includegraphics[width=0.75\textwidth]{../images/pantilt_side.png}}
	\caption{Pan Tilt Unit}
	\label{fig:pantilt}
\end{figure}
\begin{figure}
	\subfloat[Linkage Detail View]{\label{fig:pantilt_linkdetail} 
			\includegraphics[width=0.6\textwidth]{../images/pantilt_linkdetail.png}}
	\subfloat[Linkage Velocity Plots]{\label{fig:pantilt_linkplots} 
			\includegraphics[width=0.4\textwidth]{../images/pantilt_linkplot.png}}
	\caption{Tilt Linkage Detail}
	\label{fig:pantilt_link}
\end{figure}

@@

We took advantage of the MHS-PM5's swiveling lens assembly 
(see Figure \ref{fig:camera_frontview}, and added a servo actuator which could rotate the lens \degrees{135} back from straight forward, as shown in Figure \ref{fig:pantilt_linkdetail}. The tilt servo is a Hitech HS 77BB \ref{hitechs77bb}, and is capable of \degrees{180} rotation. Figures \ref{fig:pantilt} and \ref{fig:pantilt_linkdetail} show the camera lens tilted at \degrees{45} below the horizon.
The camera and tilt servo assembley is attached to the aircraft on a rotating mount. A thrust bearing takes lateral loads off the pan servo shaft, and stabilizes the assembly. The pan servo is a Hitech HS 785HB \ref{hitechhs785}, and is capable of \degrees{1260} rotation (3.5 revolutions). Both servos are powered and controlled by the Camera Control board.

The total height of the imaging system is 8.75", only 4'' of which is exposed below the fuselage of the aircraft. The rotating assembly is, on its widest dimension 2.13", and would fit inside a 2.5" cylinder. Wires exiting the side of the camera, inside the fuselage, may make the assembly a bit wider. Because the maximum rotation is only \degrees{1260}, the camera and tilt servo wires only have to be capable of wrapping \degrees{\pm 630} around the shaft below the thrust bearing. A wire guide will be added to keep the wires from tangling once construction of the pan-tilt is complete and installed in the aircraft.

The pan servo is calibrated before installation by mapping servo PWM inputs to a measured angular output at \degrees{30} intervals. Linear interpolation is used to determine PWM outputs which achieve intermediate angles. The tilt servo is calibrated at \degrees{10} intervals, due to its much smaller rotation range. As shown in Figure \ref{fig:pantilt_linkplots}, the angular accelleration of the camera angle linkage (Alpha4) is almost constant compared to the servo arm linkage throughout the range $[0^{\circ}, 135^{\circ}]$. The linkage has been designed to keep the majority of nonlinear rotation outside the camera's range of rotation. Therefore, we can consider the calibrated servo output to be directly related to the camera angle.
The endpoints of the tilt rotation rang are calibrated and enforced in software, because pushing the camera outside this range may damage it.

@@

\newpage
\appendix
\renewcommand\thesection{Appendix \Alph{section}}
\section{Preflight Procedures}
\label{sec:appendix_preflight}
\begin{enumerate}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item Assemble plane.
	\item Check all mechanical and electrical connections.
		\begin{itemize}
		\itemspace
		\item Are all nuts/bolts loc-tited?
		\item Are all servo extensions connected and properly secured?
		\item Are all access hatches secured?
		\end{itemize}
	\item Position wingmen\footnotemark, centerman\footnotemark.
	\item Pilot turns on transmitter, announces ``transmitter on.''
	\item Pilot requests ``receiver on''.  Centerman turns on receiver, acknowledges.
	\item Pilot completes surface checks:
		\begin{itemize}
		\itemspace
		\item Ailerons
		\item Elevator
		\item Rudder
		\item Throttle
		\end{itemize}
	\item Starter primes engine.
	\item Pilot obtains visual and verbal confirmation that wingmen, centerman are in place and alert.
	\item Pilot requests ``ignition on.''  Centerman moves ignition switch to the ``on'' position and acknowledges.
	\item Starter requests ``prop clear.''  Starter obtains visual confirmation that no person is standing in the prop arc and announces ``prop clear.''
	\item Starter announces ``contact'' and starts the engine.
	\item Starter clears the area.
	\item Pilot repeats surface and throttle checks at close range.
	\item Pilot leaves starting area and performs surface and throttle checks from a distance (range test).
	\item Pilot returns to starting area to prepare for taxi.
	\item Pilot requests ``centerman off.''  Centerman carefully clears the area and acknowledges.
	\item Pilot requests ``wingmen off.''  Wingmen carefully clear the area and acknowledge.
	\item Pilot taxis airplane to appropriate location to begin takeoff.
	\item Pilot commences takeoff.
